Cross-Dataset Recommender System for \\Overcoming Selection Bias

### 2022-08-17 paper/paper.tex
RMSE vs epoch
Continue paper on overleaf

% to compile a camera-ready version, add the [final] option, e.g.:
\usepackage[preprint]{neurips_2022}

@@

\usepackage[utf8]{inputenc} % allow utf-8 input
\usepackage[T1]{fontenc}    % use 8-bit T1 fonts
\usepackage{hyperref}       % hyperlinks
\usepackage{url}            % simple URL typesetting
\usepackage{booktabs}       % professional-quality tables
\usepackage{amsfonts}       % blackboard math symbols
\usepackage{nicefrac}       % compact symbols for 1/2, etc.
\usepackage{microtype}      % microtypography
\usepackage{xcolor}         % colors
\usepackage{amsmath}

@@

\title{Data-Centric Recommender System for Tackling Selection Bias-induced Distribution Shift}

@@

\begin{abstract}
  The abstract paragraph should be indented \nicefrac{1}{2}~inch (3~picas) on
  both the left- and right-hand margins. Use 10~point type, with a vertical
  spacing (leading) of 11~points.  The word \textbf{Abstract} must be centered,
  bold, and in point size 12. Two line spaces precede the abstract. The abstract
  must be limited to one paragraph.
\end{abstract}

\section{Introduction}
Selection bias is one of the most prevalent source of biases in a dataset for recommender systems. Selection bias happens when there is a pattern in the items that a user rates, either implicitly or explicitly. For example, in a recommender system for movies, users might only watch and rate the movies that are attractive to them in the first place. Selection bias is particularly relevant to recommender systems because when the system actively recommends items that the users like, it is creating bias by preventing users from accessing uncovered items. Selection bias introduces a Missing Not At Random (MNAR) condition to the observed dataset by conditioning it on the predictions of the recommender system. Tackling the selection bias in a recommender dataset has been a constant challenge in designing recommender algorithms

@@

The main contribution of this work is two-fold:
\begin{enumerate}
  \item We design experiments under a simulated environment and shows that a more quantized dataset is more susceptible to selection bias (and thus the MNAR condition.)
  \item We propose a cross-dataset learning framework that empowers existing recommender algorithms to make use of the more quantized, implicit data. \textcolor{red}{EXPLAIN MORE HERE}
\end{enumerate}

Our hypothesis and theoretical results are verified through a series of empirical evaluation in a simulated environment where users' behaviors are carefully modeled. We show that our learning framework is significantly better than baseline recommender systems that neglects selection bias. We also show that our methods are substantially better than its single-dataset counterpart. \textcolor{red}{EXPLAIN MORE HERE}

@@

\subsection{Recommender Systems Against Selection Bias}

\subsection{Quantization}

\section{Cross-Dataset Learning Framework}

@@

\subsection{Experiment Setup}

\subsection{Controlling Bias}

@@

>>>>

% to compile a camera-ready version, add the [final] option, e.g.:
\usepackage{neurips_2022}

@@

\usepackage[utf8]{inputenc} % allow utf-8 input
\usepackage[T1]{fontenc}    % use 8-bit T1 fonts
\usepackage{hyperref}       % hyperlinks
\usepackage{url}            % simple URL typesetting
\usepackage{booktabs}       % professional-quality tables
\usepackage{amsfonts}       % blackboard math symbols
\usepackage{nicefrac}       % compact symbols for 1/2, etc.
\usepackage{microtype}      % microtypography
\usepackage{xcolor}         % colors
\usepackage{amsmath}
\bibliographystyle{ksfh_nat}

@@

\title{Cross-Dataset Recommender System for \\Overcoming Selection Bias}

@@

\begin{abstract}
  The abstract paragraph should be indented \nicefrac{1}{2}~inch (3~picas) on
  both the left- and right-hand margins. Use 10~point type, with a vertical
  spacing (leading) of 11~points.  The word \textbf{Abstract} must be centered,
  bold, and in point size 12. Two line spaces precede the abstract. The abstract
  must be limited to one paragraph. The abstract paragraph should be indented \nicefrac{1}{2}~inch (3~picas) on
  both the left- and right-hand margins. Use 10~point type, with a vertical
  spacing (leading) of 11~points.  The word \textbf{Abstract} must be centered,
  bold, and in point size 12. Two line spaces precede the abstract. The abstract
  must be limited to one paragraph. testf
\end{abstract}

\section{Introduction}
Selection bias is one of the most prevalent sources of distribution shift for recommender systems. Selection bias happens when there is a pattern in the users' ratings that is unique to the training set, either implicitly or explicitly. For example, in a recommender system for movies, users might only watch and rate movies that they particularly like, while distribution the recommender system is deployed on contains all movies regardless of person al tastes. Tackling the selection bias in a recommender dataset has been a constant challenge in designing recommender algorithms

@@

The main contribution of this work is two-fold:
\begin{enumerate}
  \item We design experiments under a simulated environment and shows that susceptibility to selection bias is likely not correlated with the way a dataset is quantized.
  \item We propose a cross-dataset learning framework that empowers existing recommender algorithms to make use of the more quantized, less biased data. We carried out experiment and found our method outperforming baselines by a significant margin.
\end{enumerate}

@@

\section{Susceptibility to Selection Bias}

\subsection{Simulated Environment for Controlling Bias}

\subsection{Results}
\bibliography{refs}

\section{Cross-Dataset Propensity Estimation}

@@

\subsection{Dataset and Baselines}

@@

\section*{Acknowledgements}

\section*{References}
\bibliography{refs}
